A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

Figure~\ref{fig:PermFields} compares the permeability field for all models. The permeability field legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f)). The cases are shown without the edges for elements which discretize the domain in Fig.~\ref{fig:PermFields}(b) to (f). This highlights the fact that the permeability field in  Fig.~\ref{fig:PermFields}(c) and (d)(\ie ArithMean and HarmMean cases, respectively) are homogeneous within each block while Fig.~\ref{fig:PermFields}(e) and (f)(\ie PDFCase and SVDCase, respectively) are heterogeneous. Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase. An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability field. Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.

>>>>

Figure~\ref{fig:PermFields} compares the permeability distribution for all models. \red{Permeability legend in Fig.~\ref{fig:PermFields}(a) is representative for all the other figures (\ie Fig.~\ref{fig:PermFields}(b) to (f))} \red{(THIS INFO SHOULD BE IN THE CAPTION OF THE FIGURES INSTEAD)}. The cases are shown without the edges for elements which discretize the domain in Fig.~\ref{fig:PermFields}(b) to (f). This highlights the fact that the permeability field in  Fig.~\ref{fig:PermFields}(c) and (d)(\ie ArithMean and HarmMean cases, respectively) are homogeneous within each block while Fig.~\ref{fig:PermFields}(e) and (f)(\ie PDFCase and SVDCase, respectively) are heterogeneous. Given that the BaseCase is also heterogeneous, it can be stated that the model for the PDFCase and the SVDCase give a better representation of the BaseCase. An additional consequence of the homogeneity in the ArithMeanCase and the HarmMeanCase is that the upgrid size has no influence on the outcome of their permeability field. Whereas, for the PDFCase and the SVDCase, the permeability field will change if the upgrid resolution changes.
